---
title: "ECON 323 Assignment 3"
output: html_notebook
---

# Loading the data
```{r load}
rm(list=ls())

library(plyr)
library(dummies)
library(stargazer)
library(zoo)
library(lubridate)
library(fastDummies)

db <- read.csv("timeseries.csv", header = TRUE, stringsAsFactors = FALSE)

db2 <- subset(db, select=c(Ref_period,Current_dol_new_dwellings, Total_dwellings_num_units, Index_house, Mortgage_lending_rate))

db2$Ref_period <- as.yearmon(db2$Ref_period)
db2$year <- year(db2$Ref_period)
db2$month <- month(db2$Ref_period)

db2$Current_dol_new_dwellings <- db2$Current_dol_new_dwellings/1000

db2$t <- seq.int(nrow(db2))

db2 <- db2[, c(8,1,6,7,2,3,4,5)]

db2 <- dummy_cols(db2, select_columns="month")
```

# Doing the first regression
```{r regress}
olsreg <- lm(Current_dol_new_dwellings ~ Total_dwellings_num_units 
              + Index_house 
              + Mortgage_lending_rate, data = db2)

stargazer(olsreg, 
          title="OLS regression",
          type="text",
          digits= 4)
```

# DW test for serial correlation
```{r seri corr}
library(lmtest)
dwtest(olsreg)
```
DW returns a value smaller than the Dl value of 1.48 for n > 100 and k = 3. Therefore, we reject the null hypothesis that rho = 0 and hence, there is autocorrelation in the erros of this model. 

# Plotting to demonstrate trending
```{r plot}
library(ggplot2)
ggplot(aes(x = Ref_period, y = Current_dol_new_dwellings), data = db2) + geom_line()
```

# Regression with a linear time trend as a regressor
```{r detrend by including linear time trend regressor}
olsreg2 <- lm(Current_dol_new_dwellings ~ Total_dwellings_num_units 
              + Index_house 
              + Mortgage_lending_rate
              + t, data = db2)

stargazer(olsreg2, 
          title="OLS regression 2",
          type="text",
          digits= 4)
```

```{r seri corr 2}
dwtest(olsreg2)
```

Regression when controlling for seasonality
```{r detrend by monthly dummy variable}
olsreg3 <- lm(Current_dol_new_dwellings ~ Total_dwellings_num_units 
              + Index_house 
              + Mortgage_lending_rate
              + t
              + month_1
              + month_2
              + month_3
              + month_4
              + month_5
              + month_6
              + month_7
              + month_8
              + month_9
              + month_10
              + month_11
              + month_12
              , data = db2)

stargazer(olsreg3, 
          title="OLS regression 3",
          type="text",
          digits= 4)
```

```{r seri corr 3}
dwtest(olsreg3)
```

# Regress a lag dependent variable
```{r}
library(dynlm)
library(dyn)

Yt <- ts(db2$Current_dol_new_dwellings)
Xt <- ts(db2$Total_dwellings_num_units)
Zt <- ts(db2$Index_house)
Wt <- ts(db2$Mortgage_lending_rate)

ols4 <- dynlm(Yt ~ Xt + Zt + Wt + lag(Yt, -1), data = db2)
summary(ols4)
```

```{r test}
library(nlme)
BIC(ols4)
```




```{r something about detrend function we have yet to understand}
#library(pracma)
#db3 <- t(db2)
#data.detrend <- detrend(db3, tt = 'linear')
#data.detrend <- ts(as.numeric(data.detrend), start=c(1994, 1), end=c(2017,12), frequency=12)
#str(data.detrend)
#plot.ts(data.detrend)
```




